---
title: "InnerSource FAQ"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(shiny.i18n)
i18n <- Translator$new(translation_csvs_path = "./data")
i18n$set_translation_language("en")

knitr::opts_chunk$set(echo = FALSE)
```

<!-- # `r i18n$t("The Basics")` -->

## `r i18n$t("InnerSource FAQ")`

`r i18n$t("Here we try to address a number of frequently asked questions about InnerSource. Most of the content is courtesy of the InnerSource Commons Learning Path community:")`https://innersourcecommons.org/learn/learning-path/

## `r i18n$t("What is InnerSource?")`

`r i18n$t("InnerSource is the use of best practices from successful open source projects and establishment of an open source culture within your organization. You still develop proprietary software, while opening up work between developers and teams internally.")`

### `r i18n$t("Watch Danese Cooper and Russell Rutledge introducing InnerSource")`

![](https://youtu.be/l93ohSHhr5U)


## `r i18n$t("Why is InnerSource useful?")`

`r i18n$t("With the increasing pace of technological change, internal communication and collaboration have become key competitive differentiators, as they are both essential to agility and ensuring long-term competitive advantage.")`

`r i18n$t("Adopting InnerSource within a organization enables reuse of existing solutions and minimizes redundancy, empowers and incentivizes collaboration across teams, and makes it possible to leverage the talent across the entire workforce.")`

### `r i18n$t("Watch Russell Rutledge describe a typical situation where InnerSource is most helpful")`

![](https://www.youtube.com/watch?v=v9fL-E3ZVdc)

## `r i18n$t("What are the benefits of InnerSource?")`

`r i18n$t("Many benefits that are typical of open source development can be realized with InnerSource.")`

* **`r i18n$t("Faster, with quality:")`** `r i18n$t("Unit tests, code coverage, and continuous integration help improve code faster, producing software that is responsive and nimble to the changing needs of its many internal stakeholders.")`
* **`r i18n$t("Documentation:")`** `r i18n$t("Code is better documented, both in comments and less formally in discussions.")`
* **`r i18n$t("Code reuse:")`** `r i18n$t("Code and architecture are discoverable and available across teams and the organization.")`
* **`r i18n$t("Collaboration:")`** `r i18n$t("Friction reduced for code review, communication, and contributions in and between teams.")`
* **`r i18n$t("Culture:")`** `r i18n$t("Silos broken down, happiness improved and with that, better retainment and recruitment.")`

### `r i18n$t("Watch Russell Rutledge describe the benefits of InnerSource in further detail")`

![](https://www.youtube.com/watch?v=PFLmOWCEpi4)

## `r i18n$t("Glossary of InnerSource jargons")`

`r i18n$t("Various technical jargons used by the InnerSource community are listed here. This will help you understand various concepts and ideas about InnerSource.")`

* `r i18n$t("Silos - Silos refer to developments teams that work on a specific set of projects and rarely collaborate with other teams across the company. A few key characteristics are: A lot of shorthands and undocumented conventions about the product/codebase that is known only to that team, unwillingness to collaborate with other teams and accepting new ideas, etc.")`

* `r i18n$t("Trusted Committer - A developer outside of the product owners who has contributed to that specific product frequently and is knowledgeable about the codebase in general. They are trusted to keep the software and the community that is developing it healthy.")`



## `r i18n$t("InnerSource Quiz")`

`r i18n$t("You can attempt the following questions to test your understanding about InnerSource")`

```{r basic, echo=FALSE}
quiz(caption = i18n$t("InnerSource Knowledge Quiz"),
question(i18n$t("Which of the following options is NOT TRUE about InnerSource?"),
  answer(i18n$t("InnerSource refers to the adoption of open source best practices within an organization")),
  answer(i18n$t("InnerSource requires adopting the open source culture in terms of sharing code and collaborating with your colleagues potentially outside your depratment")),
  answer(i18n$t("Making your source code visible within the organization is enough for InnerSource"), correct = TRUE, message = i18n$t("InnerSource is not just about opening code, but more importantly about developing a culture of sharing.")),
  answer(i18n$t("InnerSource can lead to sustainable collaboration and is beneficial in ensuring the long-term success of the organization")),
  random_answer_order = TRUE,
  allow_retry = TRUE
),

question(i18n$t(" What sentence best describes the motivation for the name 'Trusted Committer?'"),
  answer(i18n$t("They are the only ones that are trusted to make commits to the project."), message = i18n$t("A good InnerSource project has a community of people submitting commits to the project. The trusted nature of the trusted committer goes beyond just raw coding activity.")),
  answer(i18n$t("It is the role name used by Apache and GitHub."), message = i18n$t("Apache and GitHub have different names for roles that encompass some of the responsibilities of the trusted committer, but not the full set. The role name of 'trusted committer' is intentionally unique to InnerSource.")),
  answer(i18n$t("They are trusted to keep the software and the community that is developing it healthy."), correct = TRUE, message = i18n$t("The role of the trusted committer is broad and encompasses subtle human interactions. After being chosen for their technical and interpersonal skills, the trusted committers employ a wide range of practices to elicit contributions, build the confidence and skills of the contributors, and ensure positive interactions throughout the community. There are no specifications for such work. It involves trust by the community and product owners.")),
  random_answer_order = TRUE,
  allow_retry = TRUE
)
)
```



